Experience-Biased Symbolic Planning

### 2014-05-12 AAAI_AuthorKit/paper.tex
Expanded notes on epsilon -> infinity

Conversely as $\epsilon^E \rightarrow\infty$, the cost remains bounded iff $S_0$ is in an E-graph component which also contains a goal state, and the minimizing path becomes the one which uses the fewest edges outside the E-graph.

>>>>

Conversely, as $\epsilon^E \rightarrow\infty$, the inflated terms dominate. Hence, the minimizing path becomes the one which incurs the least estimated cost outside the E-graph. In particular, $h^E$ has the following property:

\textit{For sufficiently large $\epsilon^E$, once the A* frontier touches an E-graph component which includes a goal state, no node outside the E-graph will ever again need to be expanded.} This means, for instance, that if the E-graph already contains a path from the start to a goal, then A* guided by $h^E$ with large bias term $\epsilon^E$ will never leave the E-graph. If the E-graph is small, a solution would promptly be discovered.
